---
title: "HEROES-Spain resilience analysis"
author: "Papoula Petri-Romão & Roberto Mediavilla"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(pacman)
p_load(tidyverse,
       psych,
       lme4,
       gtsummary)

ds <- readRDS("data/heroes_wp2_anonymised.rds")

ds_labels <- labelled::var_label(ds) # to restore labels
ds_bis <- ds # use ds <- sjlabelled::var_lables(ds_bis) to restore
```

# Pre work

```{r var transf}

# restore NAs

ds <- 
  ds %>% 
  mutate(
    across(
      .cols = where(is.factor),
      .fns = ~ fct_recode(.,
                          NULL = "-991",
                          NULL = "-992",
                          NULL = "-993")
    ),
    across(
      .cols = where(is.numeric),
      .fns = ~if_else(. < -990,
                      NA_real_,
                      .)
    )
  )

# add NAs

ds <- 
  ds %>% 
  mutate(
    ep32 = fct_recode(ep32,
                      NULL = "2", # n/a
                      NULL = "3"), # prefer not
    mp18 = fct_recode(mp18,
                      NULL = "2"), # don't know
    mp18aa =fct_recode(mp18aa,
                       NULL = "2"), # n/a
    mp18ab = fct_recode(mp18ab,
                        NULL = "2"), # don't know
    mp19 = fct_recode(mp19,
                      NULL = "4"), # n/a
    mp25a = fct_recode(mp25a,
                       NULL = "2"), # don't know
    sd03 = fct_recode(sd03,
                      NULL = "3"), # non-binary but only 10
    ep31 = fct_recode(ep31,
                      NULL = "2"), # n/a
    mp25b = fct_recode(mp25d,
                       NULL = "2", # don't know
                       NULL = "3") # n/a
    )

# aggregated outcome scores

ds <- 
  ds %>%
  mutate(ghq_total = select(., c(ad34:ad45)) %>% rowSums(),
         phq_total = select(., c(phq68:phq76)) %>% rowSums())

ds <- 
  ds %>% 
  mutate(
    across(
      starts_with("ad"),
      ~ recode(., 
               "0" = 0,               
               "1" = 0,
               "2" = 1,
               "3" = 1)
      )
    ) %>%
  mutate(ghq_score = select(.,
                       starts_with("ad")) %>% rowSums())

# BRS score

ds <- 
  ds %>% 
  mutate(
    across(
      .cols = c(re58,re60,re63),
      .fns = ~ recode(.,
                      "1" = 5,
                      "2" = 4,
                      "3" = 3,
                      "4" = 2,
                      "5" = 1) %>% 
        as.numeric
    ),
    brs_total = select(., c(re57:re63)) %>% rowSums()/6
  )
```

```{r drop fake nas}
ds %>% 
  group_by(wave) %>% 
  filter(is.na(assessment_week)) %>% 
  select(1:99) %>% 
  skimr::skim()
  
ds <- 
  ds %>% 
  drop_na(assessment_week)
```

```{r stressors coding}
ds <- 
  ds %>% 
  mutate(
    
    # HCW stressors
    
    ehc_01 = tr15,
    ehc_02 = case_when(tr16 >= 6 ~ 1,
                       tr16 < 6 ~ 0,
                       TRUE ~ NA_real_) %>% 
      as_factor(), # FIXME: remove this
    ehc_03 = case_when(tr17 >= 12 ~ 1,
                       tr17 < 12 ~ 0,
                       TRUE ~ NA_real_) %>% 
      as_factor(),
    ehc_04 = ep32,
    ehc_05 = mp18,
    ehc_06 = mp18aa, # Check?
    ehc_07 = fct_collapse(mp25c,
                         "0" = c("1", "2"),
                         "1" = c("3", "4")),
    ehc_08 = if_else(wave == "1",
                     fct_collapse(mp25d,
                                    "1" = c("1","2", "3")),
                     fct_collapse(mp25d_2and3,
                                    "0" = c("0", "1", "2"),
                                    "1" = c("3", "4"))), #TODO: keep an eye
    ehc_09 = fct_collapse(mp25e,
                          "0" = c("1", "2"),
                          "1" = c("3", "4")),
    ehc_10 = fct_recode(mp19,
                        "0" = "3",
                        "1" = "2",
                        "1" = "1",
                        "1" = "0"), #TODO: check direction
    ehc_11 = mp25a,
    
    # COVID-19 stressors
    
    ec_01 = fct_collapse(mp21,
                         "1" = c("1", "2", "3")),
    ec_02 = fct_collapse(mp23,
                         "1" = c("1", "2", "3")),
    ec_03 = mp18ab,
    ec_04 = mp24,
    ec_05 = mp25,
    ec_06 = mp25b
  )

ds <- 
  ds %>% 
  sjlabelled::var_labels(ehc_01 = "New functions",
                         ehc_02 = "Work more than 6 days",
                         ehc_03 = "Work more than 12h/day",
                         ehc_04 = "Triage decisions",
                         ehc_05 = "Frontline",
                         ehc_06 = "COVID-19 unit (waves 2 and 3)",
                         ehc_07 = "Stigma / discrimination",
                         ehc_08 = "Problems with patients' relatives",
                         ehc_09 = "Violence",
                         ehc_10 = "PPE shortages",
                         ehc_11 = "Patients passed away",
                         ec_01 = "Worry infection (self)",
                         ec_02 = "Worry infection (others)",
                         ec_03 = "Infected (waves 2 and 3)",
                         ec_04 = "Loved ones infected",
                         ec_05 = "Loved ones passed away",
                         ec_06 = "Patients passed away") 

allstressors <- 
  ds %>% 
  select(ehc_01,
         tr15,
         ehc_02,
         tr16,
         ehc_03,
         tr17,
         ehc_04,
         ep32,
         ehc_05,
         mp18,
         ehc_06,
         mp18aa,
         ehc_07,
         mp25c,
         ehc_08,
         mp25d,
         mp25d_2and3,
         ehc_09,
         mp25e,
         ehc_10,
         mp19,
         ehc_11,
         mp25a,
         ec_01,
         mp21,
         ec_02,
         mp23,
         ec_03,
         mp18ab,
         ec_04,
         mp24,
         ec_05,
         mp25,
         ec_06, 
         mp25b) %>% 
  names()

```

```{r stressors coding test, eval = FALSE}
ds %>% 
  select(matches(allstressors)) %>% 
  skimr::skim()

ds %>% 
  group_by(wave) %>% 
  select(matches(allstressors)) %>% 
  skimr::skim() # Missing values in all stressors across waves
```

Here it's very important that we rescale if needed (e.g., if one wave has
missing data on an certain item)

And this is an overview

```{r overview stressors, eval = FALSE}

# Raw stressors, outcomes, and strata

ds %>% 
  select(
    
    hashed_id,
    wave,
    
    # outcomes
    
    ghq_score,
    phq_total,
    
    # stressors
    
    tr15, # new functions
    tr16, # days/week worked
    tr17, # hours/day worked
    ep32, # prioritisation
    mp18, # frontline
    mp18aa, # covid-19 unit (waves 2 and 3)
    mp18ab, #covid-19-positive (waves 2 and 3)
    mp21, # worry (self)
    mp22, # days isolation
    mp23, # worry (others)
    mp24, # loved-ones covid-19-positive
    mp25, # loved-ones passed away
    mp25b, # patients passed away
    mp25c, # stigma / discrimination
    mp25d, # problems w/ patients' relatives (wave 1)
    mp25d_2and3, # problems w/ patients relatives (waves 2 and 3)
    mp25e, # violence
    mp19, # PPE
    mp25a, # some at work passed away (MP25a and MP25aa already harmonised)
    
    # strata
    
    sd03,
    age_cat,
    profession,
    profession_hcw,
    tr15, # medical specialty
    ra50, # soc support at work
    ra51, # soc support outside
    brs_total,
    province,
    nuts_id,
    ep31, # prioritisation instructions
    mp25g, # trust government (wave 1)
    mp25ea, # trust government (waves 2 and 3)
    mp25f, # trust workplace (wave 1)
    mp25fb, # trust work colleagues (wave 2 and 3)
    #TODO: harmonise if important longitudinally (not identical items)
    ) %>% 
  skimr::skim()

# Raw stressors, outcomes, and strata, by wave

ds %>% 
  select(
    
    #hashed_id,
    wave,
    
    # outcomes
    
    ghq_total,
    phq_total,
    
    # stressors
    
    tr15, # new functions
    tr16, # days/week worked
    tr17, # hours/day worked
    ep32, # prioritisation
    mp18, # frontline
    mp18aa, # covid-19 unit (waves 2 and 3)
    mp18ab, #covid-19-positive (waves 2 and 3)
    mp21, # worry (self)
    mp22, # days isolation
    mp23, # worry (others)
    mp24, # loved-ones covid-19-positive
    mp25, # loved-ones passed away
    mp25b, # patients passed away
    mp25c, # stigma / discrimination
    mp25d, # problems w/ patients' relatives (wave 1)
    mp25d_2and3, # problems w/ patients relatives (waves 2 and 3)
    mp25e, # violence
    mp19, # PPE
    mp25a, # some at work passed away (MP25a and MP25aa already harmonised)
    
    # strata
    
    sd03,
    age_cat,
    profession,
    profession_hcw,
    #tr15, # medical specialty
    ra50, # soc support at work
    ra51, # soc support outside
    brs_total,
    #province,
    #nuts_id,
    ep31, # prioritisation instructions
    mp25g, # trust government (wave 1)
    mp25ea, # trust government (waves 2 and 3)
    mp25f, # trust workplace (wave 1)
    mp25fb # trust work colleagues (wave 2 and 3)
  ) %>% 
  tbl_summary(.,
              by = wave)



# recoded stressors and outcomes (by wave)

ds %>% 
  select(wave,
         starts_with(c("ehc_", "ec_")),
         phq_total,
         ghq_total,
         brs_total) %>% 
  tbl_summary(., by = wave)

# corplots recoded stressors and outcomes (by wave)

ds %>% 
  filter(wave == 1) %>% 
  select(matches(allstressors)) %>% 
  mutate(
    across(
      everything(),
      ~ as.numeric(as.character(.))
    )
  ) %>% 
  cor.plot(main = "Wave 1")

ds %>% 
  filter(wave == 1) %>% 
  select(matches(allstressors)) %>% 
  mutate(
    across(
      everything(),
      ~ as.numeric(as.character(.))
    )
  ) %>% 
  cor.plot(main = "Wave 2")

ds %>% 
  filter(wave == 1) %>% 
  select(matches(allstressors)) %>% 
  mutate(
    across(
      everything(),
      ~ as.numeric(as.character(.))
    )
  ) %>% 
  cor.plot(main = "Wave 3")
```

# The mess

Descriptives show that all stressors have NAs

## First approach to calculating E scores

```{r E scores 1, eval = FALSE}
e_items <- grep("ehc_|ec_", names(ds), value = TRUE)
ehc <- grep("ehc_", names(ds), value = TRUE)
ec <- grep("ec_", names(ds), value = TRUE)

ds$ehc <- 
  psych::scoreItems(ehc, 
                    ds[ehc], 
                    totals = TRUE,
                    impute = FALSE)$scores %>% 
  as.numeric()

ds$ec <- 
  psych::scoreItems(ec, 
                    ds[ec], 
                    totals = TRUE,
                    impute = FALSE)$scores %>% 
  as.numeric()

ds$E <- 
  psych::scoreItems(e_items, 
                    ds[e_items], 
                    totals = TRUE,
                    impute = FALSE)$scores %>% 
  as.numeric()


# Check

ds %>% 
  select(hashed_id,
         wave,
         starts_with(c("ehc_", "ec_")),
         "ehc",
         "ec",
         "E")
```

The aggregated scores make no sense. Probably because we are scoring factors.

## Second approach

```{r E scores 2, eval = FALSE}
e_items <- grep("ehc_|ec_", names(ds), value = TRUE)
ehc <- grep("ehc_", names(ds), value = TRUE)
ec <- grep("ec_", names(ds), value = TRUE)

# I create an additional dataset to
# change the class of the factors

ds_num <-
  ds %>%
  mutate(
    across(
      .cols = starts_with(c("ehc_", "ec_")),
      .fns = ~ as.numeric(as.character(.))
    )
  ) %>% 
  select(hashed_id,
         wave,
         starts_with(c("ehc_", "ec_")))

# I check that this change keeps
# the true value of factors, compared to the
# original dataset

ds_num %>% 
  select(starts_with(c("ehc", "ec")))
ds %>% 
  select(starts_with(c("ehc", "ec")),
         -economic_support_index,
         -economic_support_index_for_display)

# I use the same code to calculate the scores

ds_num$ehc <- 
  psych::scoreItems(ehc, 
                    ds_num[ehc], 
                    totals = TRUE,
                    impute = FALSE)$scores %>% 
  as.numeric()



ds_num$ec <- 
  psych::scoreItems(ec, 
                    ds_num[ec], 
                    totals = TRUE,
                    impute = FALSE)$scores %>% 
  as.numeric()

ds_num$E <- 
  psych::scoreItems(e_items, 
                    ds_num[e_items], 
                    totals = TRUE,
                    impute = FALSE)$scores %>% 
  as.numeric()

# I check the supplementary dataset,
# which does not make sense either

ds_num %>% 
  select(hashed_id,
         wave,
         starts_with(c("ehc_", "ec_")),
         "ehc",
         "ec",
         "E")

```

## Third approach

I use rowSums instead of scoreItems

```{r E scores 3, eval = FALSE}
ds_num <- 
  ds %>%
  mutate(
    across(
      .cols = starts_with(c("ehc_", "ec_")),
      .fns = ~ as.numeric(as.character(.))
    )
  ) %>% 
  select(hashed_id,
         wave,
         starts_with(c("ehc_", "ec_")))

ds_num %>% 
  mutate(ehc = select(.,
                      starts_with("ehc_")) %>% rowSums(na.rm = TRUE),
         ec = select(.,
                     starts_with("ec_")) %>% rowSums(na.rm = TRUE),
         E = select(.,
                     starts_with(c("ehc_","ec_"))) %>% rowSums(na.rm = TRUE))

```

With this approach, the aggregated scores are performed correctly. The only
problem that persists is that NAs are scored as 0. One approach could be to have
a stressor count that is relative to the number of questions effectively
answered.

After this is fixed, we can use the following code

# SR scores

```{r sr scores}

# Wave 1

EP_w1 <- 
  ds %>% 
  filter(wave == 1) %>% 
  drop_na(assessment_week) %>% # TODO: remove them in the beginning
  lm(scale(phq_total) ~ poly(scale(E), 1, raw = TRUE), data = .)

EP_poly_w1 <- 
  ds %>% 
  filter(wave == 1) %>% 
  lm(scale(phq_total) ~ poly(scale(E), 2, raw = TRUE), data = .)

anova(EP_w1,EP_poly_w1,test="Chisq")

remove(EP_poly_w1)

intercept <- summary(EP_w1)$coefficients[1]
E_slope <- summary(EP_w1)$coefficients[2]

ds <- 
  ds %>% 
  mutate(P_pred = if_else(wave == 1,
                          (intercept + scale(ds$E)*E_slope),
                          NA_real_),
         SR = if_else(wave == 1,
                      scale(scale(phq_total) - P_pred),
                      NA_real_),
         RES = if_else(wave == 1,
                       -SR,
                       NA_real_)
  )

remove(intercept,
       E_slope)

# Wave 2

EP_w2 <- 
  ds %>% 
  filter(wave == 2) %>% 
  lm(scale(phq_total) ~ poly(scale(E), 1, raw = TRUE), data = .)

EP_poly_w2 <- 
  ds %>% 
  filter(wave == 2) %>% 
  lm(scale(phq_total) ~ poly(scale(E), 2, raw = TRUE), data = .)

anova(EP_w2,EP_poly_w2,test="Chisq")

intercept <- summary(EP_w2)$coefficients[1]
E_slope <- summary(EP_w2)$coefficients[2]

ds <- 
  ds %>% 
  mutate(P_pred = if_else(wave == 2,
                          (intercept + scale(ds$E)*E_slope),
                          P_pred),
         SR = if_else(wave == 2,
                      scale(scale(phq_total) - P_pred),
                      SR),
         RES = if_else(wave == 2,
                       -SR,
                       RES)
  )

remove(intercept,
       E_slope)

# Wave 3

EP_w3 <- 
  ds %>% 
  filter(wave == 3) %>% 
  lm(scale(phq_total) ~ poly(scale(E), 1, raw = TRUE), data = .)

EP_poly_w3 <- 
  ds %>% 
  filter(wave == 3) %>% 
  lm(scale(phq_total) ~ poly(scale(E), 2, raw = TRUE), data = .)

anova(EP_w3,EP_poly_w3,test="Chisq")

intercept <- summary(EP_w3)$coefficients[1]
E_slope <- summary(EP_w3)$coefficients[2]

ds <- 
  ds %>% 
  mutate(P_pred = if_else(wave == 3,
                          (intercept + scale(ds$E)*E_slope),
                          P_pred),
         SR = if_else(wave == 3,
                      scale(scale(phq_total) - P_pred),
                      SR),
         RES = if_else(wave == 3,
                       -SR,
                       RES)
  )

remove(intercept,
       E_slope)
```

```{r overview E scores}
ds %>% 
  select(allstressors,
         ehc,
         ec,
         E,
         P_pred,
         SR,
         RES) %>% 
  skimr::skim()

ds %>% 
  group_by(wave) %>% 
  select(P_pred:RES) %>% 
  skimr::skim()
```

If using ScoreItems, set impute data to FALSE

Drop NAs when filtering by wave? (something like this below)

```{r}
ds %>% 
  filter(wave == 1) %>% 
  drop_na(assessment_week)

ds %>% 
  filter(wave == 2) %>% 
  drop_na(assessment_week)

ds %>% 
  filter(wave == 3) %>% 
  drop_na(assessment_week)
```
