---
title: "heroes_dataset_wp2_v2"
author: "Roberto Mediavilla"
date: '2022-08-11'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setlocale(category = "LC_ALL", locale = "es")
```

```{r req pack, include = FALSE}
library(tidyverse)
library(lubridate)
library(naniar)
```

# Overview

Here, I prepare the full HEROES dataset (3 assessment waves) to be uploaded to OPAL, as part of RESPOND WP2 IPD meta-analysis. I will follow the [OPAL handbook for WP2](https://drzmainz.sharepoint.com/:w:/r/sites/obiba-wp2/Shared%20Documents/harmonisation/data%20upload%20preparation/handbook_datauploadprep.docx?d=w15b8e9fe38734104a507dcedc3af3d49&csf=1&web=1&e=6Hu6Lm)

## Import data

```{r collapse=TRUE}
raw_t0 <- 
  readr::read_csv2("data/20210329_heroes_t0.csv",
                  col_names = FALSE,
                  trim_ws = TRUE,
                  skip = 1)

headers <- raw_t0[1,]
colnames(raw_t0) <- headers
raw_t0 <- raw_t0[-1,]
remove(headers)

raw_t1 <- 
  readr::read_csv2("data/20210329_heroes_t1.csv",
                  col_names = FALSE,
                  trim_ws = TRUE,
                  skip = 1)

headers <- raw_t1[1,]
colnames(raw_t1) <- headers
raw_t1 <- raw_t1[-1,]
remove(headers)

raw_t2 <- 
  readr::read_csv2("data/20220526_heroes_t2.csv",
                  col_names = FALSE,
                  trim_ws = TRUE)

headers <- raw_t2[1,]
colnames(raw_t2) <- headers
raw_t2 <- raw_t2[-1,]
remove(headers)

codebook_t0 <- readxl::read_xlsx("data/heroes_codebook.xlsx",
                                 sheet = 1) %>% 
  janitor::clean_names()
codebook_t1 <- readxl::read_xlsx("data/heroes_codebook.xlsx",
                                 sheet = 2) %>% 
  janitor::clean_names()
codebook_t2 <- readxl::read_xlsx("data/heroes_codebook.xlsx",
                                 sheet = 3) %>% 
  janitor::clean_names()
```

# Include all individual participants across waves

## Remove and rename variables

### Repeated columns

I found that two of the datasets have repeated colnamnes, which will become a problem later on. Since I am not interested in those variables, I just remove them (for details, see the heroes_syntax_may_2022.Rmd file)

```{r}
raw_t0 <- 
  raw_t0 %>% 
  select(!starts_with("PCL"))
raw_t2 <- 
  raw_t2 %>% 
  select(!starts_with("BR"))
```

### Colnames at T2

Before I merge the three datasets into one, I need to remove weird prefixes from wave 3 variables

```{r}
raw_t2 <- 
  raw_t2 %>% 
  rename(`Fecha inicio` = "Fecha_inicio",
         `Fecha fin` = "Fecha_fin")

raw_t2_colnames <- colnames(raw_t2)

raw_t2_colnames_edited <- 
  str_replace(raw_t2_colnames,
            "[:alnum:]+3",
            "")

raw_t2_colnames_edited <- 
  str_replace(raw_t2_colnames_edited,
              "^_", "")

colnames(raw_t2) <- raw_t2_colnames_edited

rm(raw_t2_colnames,
   raw_t2_colnames_edited)
```

### Ps support

*This is how the psychological support section is structured at T0*

**RA52**	Selección Múltiple	Since the beginning of the pandemic, have you needed psychological support (even if you have not received it)? 	
0: No
1: Yes
**RA52a**	Selección Múltiple	Have you received in-person psychological support?
0: No
1: Yes
**RA52b**	Selección Múltiple	How much did it help you?	
0: Not at all
1: Slightly
2: Moderately
3: Considerably
4: Extremely 
**RA52c**	Selección Múltiple	Have you received long-distance psychological support (e.g. by phone, online, by video call or video conference, by chat, or through an application)? 	
0: No
1: Yes
**RA52d**	Selección Múltiple	How much did it help you?
0: Not at all
1: Slightly
2: Moderately
3: Considerably
4: Extremely 

*And this is how it is structured at T1 and T2*

RA52a	Checks	In the past three months, even if you have not received them, have you required any of the following specific supports due to the pandemic? (Select all that apply, or none)	1:00
		Psychological support	0:00
		
		RA53a	Checks	In the past three months, have you received any of the following supports due to the pandemic? (Select all that apply, or none)	1:00
		In-person psychological support 	0:00
RA53b	Checks	In the past three months, have you received any of the following supports due to the pandemic? (Select all that apply, or none)	1:00
		Long-distance psychological support (e.g., by phone, online, by video call or video conference, by chat or through an application)	0:00
		

```{r}

#TODO: eval FALSE if not working 

raw_t0 %>% 
  mutate(ps_need = RA52 %>% 
           as_factor()) -> raw_t0 # Needed psychological support

raw_t1 %>% 
  mutate(ps_need = RA52a %>% 
           as_factor()) -> raw_t1 # Needed psychological support

raw_t2 %>% 
  mutate(ps_need = RA52a %>% 
           as_factor()) -> raw_t2 # Needed psychological support

raw_t0 %>% 
  mutate(ps_inperson = as_factor(RA52a),
         ps_online= as_factor(RA52c)) -> raw_t0 # Needed psychological support

raw_t1 %>% 
  mutate(ps_inperson = as_factor(RA53a),
         ps_online= as_factor(RA53b)) -> raw_t1 # Needed psychological support

raw_t2 %>% 
  mutate(ps_inperson = as_factor(RA53a),
         ps_online= as_factor(RA53b)) -> raw_t2

raw_t1 <- 
  raw_t1 %>% 
  mutate(ps_need_rec = case_when(!is.na(RA56) & is.na(ps_need) ~ "0",
                                 is.na(RA56) & is.na(ps_need) ~ NA_character_,
                                 ps_need == "1" ~ "1",
                                 ps_need == "0" ~ "0") %>% # Check this line
           as_factor(), 
         )

raw_t2 <-  
  raw_t2 %>% 
  mutate(ps_need_rec = case_when(!is.na(RA56) & is.na(ps_need) ~ "0",
                                 is.na(RA56) & is.na(ps_need) ~ NA_character_,
                                 ps_need == "1" ~ "1",
                                 ps_need == "0" ~ "0") %>% # Check this line
           as_factor(),
         )

raw_t1 <- 
  raw_t1 %>% 
  mutate(ps_inperson_rec = case_when(!is.na(RA56) & is.na(ps_inperson) ~ "0",
                                 is.na(RA56) & is.na(ps_inperson) ~ NA_character_,
                                 ps_inperson == "1" ~ "1",
                                 ps_inperson == "0" ~ "0") %>% # Check this line
           as_factor(), 
         )

raw_t2 <-  
  raw_t2 %>% 
  mutate(ps_inperson_rec = case_when(!is.na(RA56) & is.na(ps_inperson) ~ "0",
                                 is.na(RA56) & is.na(ps_inperson) ~ NA_character_,
                                 ps_need == "1" ~ "1",
                                 ps_need == "0" ~ "0") %>% # Check this line
           as_factor(),
         )
raw_t1 <- 
  raw_t1 %>% 
  mutate(ps_online_rec = case_when(!is.na(RA56) & is.na(ps_online) ~ "0",
                                 is.na(RA56) & is.na(ps_online) ~ NA_character_,
                                 ps_online == "1" ~ "1",
                                 ps_online == "0" ~ "0") %>% # Check this line
           as_factor(), 
         )

raw_t2 <-  
  raw_t2 %>% 
  mutate(ps_online_rec = case_when(!is.na(RA56) & is.na(ps_online) ~ "0",
                                 is.na(RA56) & is.na(ps_online) ~ NA_character_,
                                 ps_online == "1" ~ "1",
                                 ps_online == "0" ~ "0") %>% # Check this line
           as_factor(),
         )
```

### MP25d

Item MP25d is impossible to harmonise across waves. 

At wave 1, it reads:

Since the beginning of the pandemic, have you experienced any problems with family members of patients with COVID-19?	0: No, no problems
	1: Yes, one problem
	2: Yes, some problems
	3: Yes, many problems 

At waves 2 and 3, it reads:

In the past three months, due to your job, have you experienced any conflictive situations (physical or verbal aggression, accusations of malpractice, etc.) with family members of patients with COVID-19?	0: Not at all
	1: Less than once a month
	2: Monthly
	3: Weekly
	4: Daily or almost daily

I create two different variables so that we can keep both in further analysis. MP25d stays as it is for wave one, but MP25d_2and3 is created for waves 2 and 3.

```{r}
raw_t1<- 
  raw_t1 %>% 
  rename(MP25d_2and3 = MP25d)

raw_t2 <- 
  raw_t2 %>% 
  rename(MP25d_2and3 = MP25d)
```

### Bind rows

```{r}
df <- 
  bind_rows(raw_t0, 
            raw_t1,
            raw_t2,
          .id = "wave")
```

## Remove observations

I delete ~ 200 observations that I know are not valid

```{r}
df <- 
  df %>% 
  filter(wave == "3" | 
           `Fecha inicio` <= "2020-06-22 02:00:00" | 
           `Fecha inicio`>= "2021-01-26 00:00:00",
         !ID %in% c("2", "3", "60", "160", "275", "536", "1778", "7221"),
         !is.na(SD01))
```

## Add observations

I need to make sure that each unique Identifier is represented three times in the dataset, regardless of whether they completed one, two, or three assessment waves.

```{r}
df %>% 
  select(Identificador) %>% 
  group_by(Identificador) %>% 
  summarise(n = n()) -> unique_ids

unique_ids <- 
  unique_ids %>% 
  select(Identificador)

raw_t0_complete <- 
  right_join(raw_t0,
             unique_ids,
             by = "Identificador")

raw_t1_complete <- 
  right_join(raw_t1,
             unique_ids,
             by = "Identificador")

raw_t2_complete <- 
  right_join(raw_t2,
             unique_ids,
             by = "Identificador")
```

## Complete dataset

```{r}
df <- 
  bind_rows(raw_t0_complete, 
            raw_t1_complete,
            raw_t2_complete,
            .id = "wave")
```

# Create new variables

## Lockdown stringency index

All variables added, as per latest version of RESPOND handbook (16 November 2022).

```{r}
stringency_index <- 
  readr::read_csv("https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker/master/data/OxCGRT_nat_latest.csv") %>% 
  filter(CountryCode == "ESP")

stringency_index <- 
  stringency_index %>% 
  mutate(date = ymd(Date)) %>% 
  select(!Date)

df <- df %>% 
  mutate(date = as_date(`Fecha inicio`))

df_str <- left_join(df,
                    stringency_index,
                    by = "date")

rm(stringency_index)
```

## Income quartiles and quintiles

```{r}
income <- 
  tibble(
  year = as.double(c("2018", "2019", "2020")), # Only 2020 applies
  quintile_1 = c(8549, 8847, 9449),
  quintile_2 = c(12647,12997,13840),
  quintile_3 = c(17064,17422,18526),
  quintile_4 = c(23666,24104,25189),
  quartile_1 = c(9509,9816,10562),
  quartile_2 = c(14785,15015,16043),
  quartile_3 = c(21656,22024,23295)
)

df_str <- 
  df_str %>% 
  mutate(year = year(date))

df_str <- 
  left_join(df_str,
            income,
            by = "year")

rm(income)
```

## Google Mobility / NUTS

### Relational data

I need to merge the data from the Google Mobility report with my dataset. For that purpose, I need four relational datasets.

```{r}
mobility <- 
  readr::read_delim("data/2022_ES_Region_Mobility_Report.csv",
                    delim = ",")
```

```{r collapse=TRUE}
mobility %>% 
  select(sub_region_1) %>% 
  table() # CCAA
mobility %>% 
  select(sub_region_2) %>% 
  table() # Province
```

In the mobility dataset, I am interested in the "sub_region_2" variable, which is also included in the NUTS dataset. I edited the NUTS dataset before reading it to simplify the process

```{r}
nuts_provinces <- 
  readxl::read_xlsx("data/nuts_level_3_provinces.xlsx")
```

```{r}
nuts_urbanrural <- 
  readxl::read_xlsx("data/nuts_urbanrural.xlsx")
```

```{r}
nuts_urbanruralremoteness <- 
  readxl::read_xlsx("data/nuts_urbanruralremoteness.xlsx")
```

Now I can link the outcomes from Google and NUTS.

```{r}
nuts_pc <- 
  readr::read_delim("data/pc2020_ES_NUTS-2021_v1.0.csv",
                    delim = ";")
```

```{r}
nuts_pc <- 
  nuts_pc %>% 
  mutate(NUTS3 = str_replace_all(NUTS3,
                                   "'",
                                   ""),
         CODE  = str_replace_all(CODE,
                                   "'",
                                   "")
  )
```

And now I can link outcomes from Google and NUTS with my df through postcodes

To do so, I will first merge all the NUTS datasets

```{r collapse=TRUE}
str(nuts_pc)
str(nuts_provinces)
str(nuts_urbanrural)
str(nuts_urbanruralremoteness)
```

```{r}
nuts_pc  <- 
  nuts_pc %>% 
  rename(nuts_id = NUTS3,
         SD01a = CODE)
nuts_urbanrural <- 
  nuts_urbanrural %>% 
  rename(nuts_id = NUTS_ID,
         nuts_urbanrural_category = `URBAN-RURAL CATEGORY`,
         nuts_urbanrural_label = `URBAN-RURAL LABEL`)
nuts_urbanruralremoteness <- 
  nuts_urbanruralremoteness %>% 
  rename(nuts_id = `NUTS ID`,
         nuts_remoteness_category = `CATEGORY CODE`,
         nuts_remoteness_label = `CATEGORY LABEL`)
nuts_provinces <- 
  nuts_provinces %>% 
  rename(nuts_id = `Code 2021`,
         province = `NUTS level 3`)
```

Succesive merging

```{r}
nuts_ds <- 
  left_join(nuts_pc,
          nuts_provinces,
          by = "nuts_id") %>% 
  left_join(.,
            nuts_urbanrural,
            by = "nuts_id") %>% 
  left_join(.,
            nuts_urbanruralremoteness,
            by = "nuts_id")
```

```{r}
rm(nuts_pc,
   nuts_provinces,
   nuts_urbanrural,
   nuts_urbanruralremoteness)
```

```{r}
mobility %>% 
  filter(!sub_region_2 %in% nuts_ds$province) %>% 
  select(sub_region_2) %>% 
  table() # I need to change these names
nuts_ds$province %>% table()
```

```{r}
mobility %>% 
  mutate(sub_region_2 = str_replace_all(sub_region_2,
                                            "Álava",
                                            "Araba/Álava"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Alicante",
                                    "Alacant/Alicante"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Biscay",
                                    "Bizkaia"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Castellón",
                                    "Castellón/Castelló"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Las Palmas",
                                    "Gran Canaria"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Santa Cruz de Tenerife",
                                    "Tenerife"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Province of Ourense",
                                    "Ourense"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Seville",
                                    "Sevilla"),
         sub_region_2 = str_replace_all(sub_region_2,
                                    "Valencia",
                                    "Valencia/València")
         ) %>%
  rename(province = sub_region_2) -> mobility
```

### Add info to the main dataset

```{r}
df_str <- 
  left_join(df_str,
            nuts_ds,
            by = "SD01a")
rm(nuts_ds)
```

```{r}
left_join(df_str,
          mobility,
          by = c("date", "province"))
```

The number of rows gets higher when I merge these two datasets. I think that is because there are several NAs in the mobility dataset

```{r}
mobility %>% 
  mutate(province = as.factor(province)) %>% 
  select(province) %>% 
  group_by(province) %>% 
  count() %>% 
  data.frame # 4340 NAs
```

```{r}
mobility_red <- 
  mobility %>% 
  select(date:province) %>% 
  filter(!is.na(province))
```

```{r}
df_str <- 
  left_join(df_str,
          mobility_red,
          by = c("date", "province"))

rm(mobility,
   mobility_red)
```

## UN country/region codes

Based on updated handbook (16 November 2022)

```{r}
df_str <- 
  df_str %>% 
  mutate(
    m49_region = "150" %>% as_factor,
    m49_subregion = "039" %>% as_factor
  )
```


# Variable transformation

## Variable dictionaries

I do not use OPAL for this. According to the vardict file, #5 should be "Date of Birth", which we consider sensitive data and thus will not upload (see below).

```{r}
df_str <- 
  df_str %>% 
  mutate(SD03 = case_when(SD03 == "0" ~ "2",
                          SD03 == "1" ~ "1",
                          SD03 == "2" ~ "3"),
         country_of_residence = factor("ES",
                                       levels = "ES"),
         migration = NA_integer_,
         age_cat = case_when(EDAD < 18 ~ "below 18 years",
                             EDAD > 17 & EDAD < 45 ~ "18-44",
                             EDAD > 44 & EDAD < 65 ~ "45-64",
                             EDAD > 64 & EDAD < 95 ~ "65-94",
                             EDAD > 94 ~ "95 years or older",
                             EDADV2 < 18 ~ "below 18 years",
                             EDADV2 > 17 & EDADV2 < 45 ~ "18-44",
                             EDADV2 > 44 & EDADV2 < 65 ~ "45-64",
                             EDADV2 > 64 & EDADV2 < 95 ~ "65-94",
                             EDADV2 > 94 ~ "95 years or older"),
         employment_status = as.integer(1),
         contract = NA_integer_,
         employment_type = NA_integer_,
         healthcare_worker = 1,
         profession = case_when(TR14 == "1" ~ "4",
                                TR14 == "2" ~ "4",
                                TR14 == "3" ~ "4",
                                TR14 == "4" ~ "4",
                                TR14 == "5" ~ "4",
                                TR14 == "6" ~ "4",
                                TR14 == "7" ~ "4",
                                TR14 == "8" ~ "4",
                                TR14 == "9" ~ "4",
                                TR14 == "10" ~ "4",
                                TR14 == "11" ~ "4",
                                TR14 == "12" ~ "4",
                                TR14 == "13" ~ "4",
                                TR14 == "14" ~ "4",
                                TR14 == "15" ~ "5",
                                TR14 == "16" ~ "4",
                                TR14 == "17" ~ "4",
                                TR14 == "18" ~ "14",
                                TR14 == "19" ~ "11",
                                TR14 == "20" ~ "10",
                                TR14 == "21" ~ "12",
                                TR14 == "22" ~ "12",
                                TR14 == "23" ~ "12",
                                TR14 == "24" ~ "14",
                                TR14 == "25" ~ "4",
                                TR14 == "26" ~ "4",
                                TR14 == "27" ~ "14",
                                TR14 == "28" ~ "14",
                                TR14 == "29" ~ "14",
                                TR14 == "30" ~ "14",
                                TR14 == "31" ~ "4"),
         education = case_when(SD04 == "0" ~ "4",
                               SD04 == "1" ~ "1",
                               SD04 == "2" ~ "2",
                               SD04 >= "3" ~ "3"),
         relationship_status = NA_integer_,
         children = if_else(SD08 == "0",
                            "2",
                            SD08),
         children_household = if_else(SD08 == "0",
                                      "2",
                                      SD08),
         children_n = case_when(SD08a == "0" ~ "1",
                                SD08a == "1" ~ "2",
                                SD08a == "2" ~ "3",
                                SD08a == "3" ~ "3",
                                SD08a > "3" ~ "4"), #TODO: check w Pap
         living_alone = if_else(SD07 == "1",
                                "1",
                                "2"), # recoded before it was 0
         household_size = case_when(SD07 == "01" ~ "1",
                                    SD07 == "02" ~ "2",
                                    SD07 == "04" ~ "4",
                                    SD07 == "1" ~ "1",
                                    SD07 == "2" ~ "2",
                                    SD07 == "3" ~ "3",
                                    SD07 == "4" ~ "3",
                                    SD07 > "4" & SD07 < 10 ~ "4",
                                    SD07 > "9" ~ NA_character_)
         ) 
```

## Additional recodings

### Profession - HCWs only

Since our dataset includes HCWs only, I include an additional categorisation of professions to better capture the nature of our data.

```{r job hcws}
df_str <- 
  df_str %>%
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "farm|FARM|Farm"),
                        "25")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "bio|Bio|BIO|bió|Bió|BIÓ"),
                        "26")) %>%
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "administr|Administr|ADMINISTR"),
                        "18")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "Enfermer|enfermer|ENFERMER"),
                        "2")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "Matr|matr|MATR"),
                        "13")) %>%
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "Psic|psic|PSIC"),
                        "4")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "elador|ELADOR"),
                        "19")) %>%
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "OGOP|ogop"),
                        "14")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "avand|Barb|barb|encer"),
                        "21")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "isiot|ISIOT"),
                        "8")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "rabaj|RABAJ"),
                        "5")) %>%   
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "ASTREAD|astread"),
                        "31")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "edic|édic|EDIC|ÉDIC"),
                        "1")) %>%
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "siq"),
                        "1")) %>%  
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "onito|ONITO"),
                        "30")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "duca|DUCA"),
                        "30")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "uida|UIDA"),
                        "30")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "residencia|RESIDENCIA|Residencia|
                                   residencial|Residencial|RESIDENCIAL"),
                        "30")) %>% 
  mutate(TR14 = replace(TR14,
                        str_detect(TR14tex,
                                   "faisem|FAISEM|Faisem"),
                        "30"))

df_str <- 
  df_str %>% 
  mutate(
    profession_hcw = fct_collapse(TR14,
                                  "physician" = "1",
                                  "nurse" = c("2","13"),
                                  "health technician" = c("3","6","7"),
                                  "ancillary worker" = c("18":"23"),
                                  "other HCW" = c("4","5","8","9","10","11",
                                                "12","14","15","25","26","31"),
                                  "socio-community" = c("27","28", "29","30"),
                                  "other" = c("16","17","24")
                           
    )
  )
```

### Outliers

```{r}
df_str <- 
  df_str %>% 
  mutate(TR16 = as.numeric(TR16),
         TR16 = if_else(TR16 > 7,
                        NA_real_,
                        TR16),
         TR17 = as.numeric(TR17) %>% round(0),
         TR17 = if_else(TR17 > 24,
                        NA_real_,
                        TR17))
```


## Dates and times

I will change the exact date and use the week number instead

```{r}
df_str <- 
  df_str %>% 
  mutate(
    across(
      .cols = c(`Fecha inicio`, `Fecha fin`),
      .fns = ymd_hms
    ),
    assessment_week = isoweek(`Fecha inicio`),
    assessment_year = year(`Fecha inicio`)
  )
```

```{r eval = FALSE}
df_str %>% 
  mutate(assessment_week = isoweek(`Fecha inicio`),
         assessment_year = year(`Fecha inicio`)) %>% 
  select(assessment_week,
         assessment_year) %>% 
  group_by(assessment_week,
           assessment_year) %>% 
  count() %>% 
    arrange(assessment_year) # makes sense
```

## Other sensitive variables

```{r}
df_str <- 
  df_str %>% 
  mutate(
    across(
      .cols = c(`Fecha inicio`,
                `Fecha fin`,
                SD01a,
                EDAD,
                EDADV2,
                EDADRCH,
                EDADRCHV2,
                contains("tex"),
                contains("esp") & !SD08new_esp, # Number of people under care
                SP67,
                SD11a,
                SD11b,
                date),
      ~ NA_character_
    )
  )
```  

# Eliminate unnecesary variables

Variables with 100% missing data

```{r}
miss_var_summary(df_str) %>% 
  filter(pct_miss > 99.9) %>% 
  select(variable) -> df_str_100_missing

df_str <- 
  df_str %>% 
  select(!all_of(df_str_100_missing$variable))
```

Variables not included in the RESPOND WP2 codebook

```{r}
# New version (1.12.22)

vv_respond_opal <- 
  readxl::read_xlsx("heroes_respond_varlist.xlsx")

df_str_red <- 
  df_str %>% 
  select(wave,
         Identificador,
         any_of(vv_respond_opal$variable),
         CountryName:assessment_year)
```


```{r eval = FALSE}
vv_respond_opal <- 
  readxl::read_xlsx("data/vv_codebook_opal.xlsx", 
                    #TODO: read from variable list instead when ready
                    col_names = F)

df_str %>% 
  select(any_of(vv_respond_opal$...1)) # 119 / 130 variables already in the dataset

vv_respond_opal %>% 
  select(...1) %>% 
  filter(!...1 %in% colnames(df_str))

#FIXME: remove if works
```

EDAD and EDAD_V2 have already been deleted. Suicidality variables ("IS") are not collected in Spain. RE61 does not exist (surprisingly). SD01a was removed. The only problem is SD08new_esp, where respondents specify how many people they had under their care (which I already fixed)

```{r eval = FALSE}
df_str_red <- 
  df_str %>% 
  select(wave,
         Identificador,
         profession_hcw,
         SD01,
         EP31,
         
         MP25a, # TODO: update var list and remove
         MP19, #TODO: update var list and remove
         any_of(vv_respond_opal$...1),
         starts_with("ps_"), # TODO: remove if not working
         CountryName:assessment_year)

#FIXME: remove if works
```

# Recode NAs

I will first get a description of missing values

```{r eval = FALSE}
df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100) %>% 
  data.frame
```

Two variables can be recoded using -992 ("I prefer not to respond")

```{r}
df_str_red %>% 
  mutate(EP32 = fct_recode(EP32,
                           "-992" = "3"),
         EP32a = fct_recode(EP32a,
                            "-992" = "4")) %>% 
  select(starts_with("EP32"))
```


```{r}
#FIXME: Set to FALSE while I work on the stressors
all_miss_wave1 <- 
  df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100,
         wave == 1) %>% 
  ungroup() %>% 
  select(variable)

all_miss_wave2 <- 
  df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100,
         wave == 2) %>% 
  ungroup() %>% 
  select(variable)

all_miss_wave3 <- 
  df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100,
         wave == 3) %>% 
  ungroup() %>% 
  select(variable)

df_str_red_chr <- 
  df_str_red %>%
  
  # I do this first to make the code work
  
  mutate(
    across(
      .cols = everything(),
      .fns = as.character
    )
  ) %>% 
  
  # I recode the system missing values first
  
  mutate(
    across(
      .cols = all_of(all_miss_wave1$variable),
      .fns = ~if_else(wave=="1",
                        "-991",
                        .)
    ),
    across(
      .cols = all_of(all_miss_wave2$variable),
      .fns = ~if_else(wave=="2",
                      "-991",
                      .)
    ),
    across(
      .cols = all_of(all_miss_wave3$variable),
      .fns = ~if_else(wave=="3",
                      "-991",
                      .)
    ),
    
    # And then the response missing values
    
    across(
      .cols = everything(),
      .fns = ~replace_na(., "-993")
    )
  )
```

```{r eval = FALSE}
#FIXME: working on this so that I can easily use it with factors (I don't have chr in my dataset anymore)

all_miss_wave1 <- 
  df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100,
         wave == 1) %>% 
  ungroup() %>% 
  select(variable)

all_miss_wave2 <- 
  df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100,
         wave == 2) %>% 
  ungroup() %>% 
  select(variable)

all_miss_wave3 <- 
  df_str_red %>% 
  group_by(wave) %>% 
  miss_var_summary() %>% 
  filter(pct_miss == 100,
         wave == 3) %>% 
  ungroup() %>% 
  select(variable)

df_str_red_rec <- 
  df_str_red %>% 
  mutate( # I must first recode all variables into chr so that if_else works properly
    across(
      .cols = all_of(all_miss_wave1$variable),
      .fns = as.character
    ),
    across(
      .cols = all_of(all_miss_wave2$variable),
      .fns = as.character
    ),
    across(
      .cols = all_of(all_miss_wave3$variable),
      .fns = as.character
  )  
  ) %>% 
  mutate( # here, I recode all variables at once
    across(
      .cols = all_of(all_miss_wave1$variable),
      .fns = ~if_else(wave==1,
                      "-991",
                      .)
    ),
    across(
      .cols = all_of(all_miss_wave2$variable),
      .fns = ~if_else(wave==2,
                      "-991",
                      .)
    ),
    across(
      .cols = all_of(all_miss_wave3$variable),
      .fns = ~if_else(wave==3,
                      "-991",
                      .)
    ),
    across(
      .cols = where(is.factor),
      .fns = ~fct_recode(.,
                        "-993" = NA_character_)
    ),
    across(
    across(
      .cols = where(is.character),
      .fns = ~replace_na(., "-993")
    ),
      .cols = where(is.numeric),
      .fns = ~ replace_na(., -993)
    )
  )

rm(all_miss_wave1,
   all_miss_wave2,
   all_miss_wave3)
```

# Set variable class

```{r}
df_str_red <- 
  df_str_red_chr %>% 
  mutate(
    across(
      .cols = c(MP22,
                SD07,
                SD08a,
                TR16,
                TR17),
      .fns = ~ str_extract(., ".[:digit:]*") %>% as.numeric
    ),
    across(
      .cols = c(starts_with(c("AD",
                              "GAD",
                              "PCPTSD",
                              "PHQ")),
                RE57:RE63),
      .fns = as.numeric),
    across(
      .cols = CountryName:quartile_3,
      .fns = as.numeric
    )
    ) %>% 
  mutate(
    across(
      .cols = where(is.character) & !Identificador,
      .fns = as.factor
    )
  )

miss_var_summary(df_str_red) %>% 
  filter(pct_miss > 0) %>% 
  select(variable) -> for_rec # See that new NAs pop up now

df_str_red <- 
  df_str_red %>% 
  mutate(
    across(
      .cols = all_of(for_rec$variable),
      .fns = ~replace_na(., -991)
    )
  )
```

# Set variable labels

```{r eval = FALSE}
# test OK

lab_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  drop_na() %>% 
  filter(short_name %in% colnames(df_str_red))

test <- 
  df_str_red_anonymised %>% 
  select(all_of(lab_t0$short_name)) %>% 
  sjlabelled::set_label(., lab_t0$item)

str(test)

# mutate

test2 <- 
  df_str_red_anonymised %>% 
  mutate(
    across(
      .cols = all_of(lab_t0$short_name),
      .fns = ~sjlabelled::set_label(.,lab_t0$item)
    )
  )

str(test2) #FIXME: to get labels in the future
```

Intento crear un vector que me permita hacer esto

```{r eval = FALSE}
labelled::var_label(iris) <- list(Petal.Length = "Length of petal", Petal.Width = "Width of Petal")
labelled::var_label(iris) <- list(Petal.Length = 'Length of petal', Petal.Width = 'Width of Petal')

iris_tibble <- as_tibble(iris)

labelled::var_label(iris_tibble) <- list(Petal.Length = 'Length of petal', Petal.Width = 'Width of Petal')
```

```{r eval = FALSE}
labs_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  drop_na() %>% 
  mutate(
    item = paste0("'", item,"'"),
    combi = paste0(short_name, " = ",item)
  ) %>% 
  select(combi)

labs_t0

# 2

labs_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  drop_na() %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t1 <- 
  codebook_t1 %>% 
  select(short_name, item) %>% 
  drop_na() %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t2 <- 
  codebook_t2 %>% 
  select(short_name, item) %>% 
  drop_na() %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs <- 
  c(labs_t0,
    labs_t1,
    labs_t2)

# 3

labs_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(df_str_red)) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labelled::var_label(df_str_red) <- labs_t0 #WORKS

# EXPORT OP 1

labs_t1 <- 
  codebook_t1 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(df_str_red)) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))
labs_t2 <- 
  codebook_t2 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(df_str_red)) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labelled::var_label(df_str_red) <- labs_t1
labelled::var_label(df_str_red) <- labs_t2
```

Solución: necesito tres vectores con  los colnames específicos de cada ola

```{r eval = FALSE}
labs_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(raw_t0)) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t1 <- 
  codebook_t1 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(raw_t1) & 
           !short_name %in% colnames(c(raw_t0, raw_t2))) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t2 <- 
  codebook_t2 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(raw_t2) & 
           !short_name %in% colnames(c(raw_t0, raw_t1))) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t1_only <- labs_t1 %>% filter(!labs_t1 %in% labs_t0)

```

```{r eval = FALSE}
labs_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(raw_t0))

labs_t1 <- 
  codebook_t1 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(raw_t1) & 
           !short_name %in% colnames())

labs_t2 <- 
  codebook_t2 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% colnames(raw_t2) & 
           !short_name %in% colnames(c(raw_t1, raw_t2)))
```

```{r}
# Step 1. Get colnames

raw_t0 %>% 
  select(ends_with(colnames(df_str_red))) %>% 
  colnames() -> t0_uniq

raw_t1 %>% 
  select(matches(colnames(df_str_red))) %>% 
  select(!matches(t0_uniq)) %>% 
  colnames() -> t1_uniq

raw_t2 %>% 
  select(matches(colnames(df_str_red))) %>% 
  select(!matches(t0_uniq)) %>% 
  select(!matches(t1_uniq)) %>% 
  rename_with(.,
              ~ str_replace(.,
                    "[:alnum:]+3_",
                    "")) %>% 
  colnames() -> t2_uniq

df_str_red %>% 
  select(!matches(t0_uniq)) %>% 
  select(!matches(t1_uniq)) %>% 
  select(!matches(t2_uniq)) %>% 
  colnames() -> new

# Tengo 130 variables (en df_str_red hay 206)

labs_t0 <- 
  codebook_t0 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% t0_uniq) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t1 <- 
  codebook_t1 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% t1_uniq) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_t2 <- 
  codebook_t2 %>% 
  select(short_name, item) %>% 
  filter(short_name %in% t2_uniq) %>% 
  with(.,
       split(item,
             factor(short_name, levels = unique(short_name))))

labs_new <- 
  new %>% 
  as_tibble() %>% 
  mutate(short_name = value,
         item = "unknown") %>% 
  select(!value) %>% 
  with(.,
     split(item,
           factor(short_name, levels = unique(short_name))))

labs <- c(labs_t0, labs_t1, labs_t2, labs_new)

# labelled::var_label(df_str_red) <- labs_new
# labelled::var_label(df_str_red) <- labs_t2
# labelled::var_label(df_str_red) <- labs_t1
# labelled::var_label(df_str_red) <- labs_t0 

labelled::var_label(df_str_red) <- labs

labelled::var_label(df_str_red) #CHECK
```

# Create hash ID

The WP2 handbook for harmonisation reads that a unique identifier (random integer) should be assigned to each participant. To secure that process, I will first create a hashed ID, remove the original ID, and then transform that new ID in a random integer.

```{r}
library(openssl)

df_str_red %>% 
  mutate(hashed_id = md5(Identificador)) -> df_str_red

df_str_red_anonymised <- 
  df_str_red %>% 
  select(!Identificador) %>% 
  relocate(hashed_id)
```

# Clean variable names

```{r}
df_str_red_anonymised %>% 
  janitor::clean_names(.) -> df_str_red_anonymised
```

# Save Rdata

```{r eval = FALSE}
saveRDS(df_str_red_anonymised, "data/heroes_wp2_anonymised.rds")
df_rds <- readRDS("data/heroes_wp2_anonymised.rds")
```

```{r eval = FALSE}
haven::write_sav(df_str_red_anonymised, "test_3.sav")
```

# Save .csv

```{r eval = FALSE}
write_csv(df_str_red_anonymised, "heroes_wp2_anonymised.csv")
```

